---
title: "Bai2025-Empirical Evidence"
author: "Bing Bai"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(lfe)
library(stargazer)
library(ggplot2)
```


#### Load Data ####
```{r}
load("Data_simulated/Bai2025_agg_synthetic_data.rda")
```

#### Table 1: Note that the primary dataset is aggregated at the location-day level. The package-level attributes reported in Table 1 are directly sourced from the platform’s proprietary database.

#### Define Treatment Group and Post-Period Indicators ####
```{r}
# Binary indicator for whether location i is within 0.4 km of a newly opened station (treated group)
data$Station <- ifelse(data$distance <= 0.4, 1, 0)

# Binary indicator for whether the observation occurs after the station opening (post-treatment period)
data$After <- ifelse(data$Days >= 0, 1, 0)

```


### Table 2: Impact of Pick-up Stations ###
```{r warning=FALSE}
# Estimate models
est_sum     <- felm(GMV ~ After + Station * After | town_id + year_week + week_day, data)
est_avg     <- felm(Items_value ~ After + Station * After | town_id + year_week + week_day, data)
est_num     <- felm(Orders ~ After + Station * After | town_id + year_week + week_day, data)
est_newcus  <- felm(Newcomers ~ After + Station * After | town_id + year_week + week_day, data)

# Averages of DVs
avg_GMV         <- mean(data$GMV)
avg_Items_value <- mean(data$Items_value, na.rm=TRUE)
avg_Orders      <- mean(data$Orders)
avg_Newcomers   <- mean(data$Newcomers)

# Extract interaction coefficients
interact_sum     <- coef(est_sum)["After:Station"]
interact_avg     <- coef(est_avg)["After:Station"]
interact_num     <- coef(est_num)["After:Station"]
interact_newcus  <- coef(est_newcus)["After:Station"]

# Compute relative effect sizes
rel_eff_sum     <- round(100 * interact_sum / avg_GMV, 1)
rel_eff_avg     <- round(100 * interact_avg / avg_Items_value, 1)
rel_eff_num     <- round(100 * interact_num / avg_Orders, 1)
rel_eff_newcus  <- round(100 * interact_newcus / avg_Newcomers, 1)

# Create custom add.lines for extra rows
add_lines <- list(
  c("Relative Effect Size", 
    paste0(rel_eff_sum, "\\%"), 
    paste0(rel_eff_avg, "\\%"), 
    paste0(rel_eff_num, "\\%"), 
    paste0(rel_eff_newcus, "\\%")),
  c("Time fixed effects", "Yes", "Yes", "Yes", "Yes"),
  c("Area fixed effects", "Yes", "Yes", "Yes", "Yes")
)

# Format average note dynamically
note_avg <- paste0(
  "Note: Average of \\textit{GMV} was ", round(avg_GMV, 3), 
  ", average of \\textit{Items value} was ", round(avg_Items_value, 3), 
  ", average of \\textit{Orders} was ", round(avg_Orders, 3), 
  ", average of \\textit{Newcomers} was ", round(avg_Newcomers, 3), "."
)

# Generate output for Table 2
stargazer(est_sum, est_avg, est_num, est_newcus,
  star.cutoffs = c(0.05, 0.01, 0.001),
  type = "text",
  no.space = TRUE,
  keep = c("After", "Station", "After:Station"),
  keep.stat = "n",
  column.labels = c("GMV", "Items value", "Orders", "Newcomers"),
  dep.var.labels.include = FALSE,
  title = "Table 2: Impact of Pick-up Stations",
  label = "main_table",
  table.placement = "H",
  font.size = "scriptsize",
  add.lines = add_lines,
  notes = note_avg,
  notes.align = "l"
)
```
#### Parallel Trend Test ####
```{r warning=FALSE}
# Subset pre-treatment data
data_prior <- filter(data, Days < 0)

# Estimate models
est_sum     <- felm(GMV ~ Days + Days * Station | town_id + year_week + week_day, data_prior)
est_avg     <- felm(Items_value ~ Days + Days * Station | town_id + year_week + week_day, data_prior)
est_num     <- felm(Orders ~ Days + Days * Station | town_id + year_week + week_day, data_prior)
est_newcus  <- felm(Newcomers ~ Days + Days * Station | town_id + year_week + week_day, data_prior)

# Averages of DVs (in the pre-period)
avg_GMV         <- mean(data_prior$GMV)
avg_Items_value <- mean(data_prior$Items_value, na.rm = TRUE)
avg_Orders      <- mean(data_prior$Orders)
avg_Newcomers   <- mean(data_prior$Newcomers)

# Extract interaction coefficients
interact_sum     <- coef(est_sum)["Days:Station"]
interact_avg     <- coef(est_avg)["Days:Station"]
interact_num     <- coef(est_num)["Days:Station"]
interact_newcus  <- coef(est_newcus)["Days:Station"]

# Compute relative effect sizes
rel_eff_sum     <- round(100 * interact_sum / avg_GMV, 2)
rel_eff_avg     <- round(100 * interact_avg / avg_Items_value, 2)
rel_eff_num     <- round(100 * interact_num / avg_Orders, 2)
rel_eff_newcus  <- ifelse(interact_newcus < 0.0001, "<0.01", round(100 * interact_newcus / avg_Newcomers, 2))

# Create custom add.lines for extra rows
add_lines <- list(
  c("Relative Effect Size", 
    paste0(rel_eff_sum, "\\%"), 
    paste0(rel_eff_avg, "\\%"), 
    paste0(rel_eff_num, "\\%"), 
    paste0(rel_eff_newcus, "\\%")),
  c("Time fixed effects", "Yes", "Yes", "Yes", "Yes"),
  c("Area fixed effects", "Yes", "Yes", "Yes", "Yes")
)

# Format average note dynamically
note_avg <- paste0(
  "Note: Average of \\textit{GMV} was ", round(avg_GMV, 3), 
  ", average of \\textit{Items value} was ", round(avg_Items_value, 3), 
  ", average of \\textit{Orders} was ", round(avg_Orders, 3), 
  ", average of \\textit{Newcomers} was ", round(avg_Newcomers, 3), "."
)

# Generate output for Table 11
stargazer(est_sum, est_avg, est_num, est_newcus,
  star.cutoffs = c(0.05, 0.01, 0.001),
  type = "text",
  no.space = TRUE,
  keep = c("Days", "Station", "Days:Station"),
  keep.stat = "n",
  column.labels = c("GMV", "Items value", "Orders", "Newcomers"),
  dep.var.labels.include = FALSE,
  title = "Parallel Trend Test",
  label = "test_parallel",
  table.placement = "H",
  font.size = "scriptsize",
  add.lines = add_lines,
  notes = note_avg,
  notes.align = "l"
)

```





#### Robustness Check: GMV and Orders by Treatment Distance ####
```{r warning=FALSE}
# Define treatment distances to test
treat_dists <- c(0.25, 0.3, 0.35, 0.4)
gmv_models <- list()
order_models <- list()

# Loop through treatment distances
for (d in treat_dists) {
  data$Station <- ifelse(data$distance <= d, 1, 0)
  
  gmv_models[[as.character(d)]] <- felm(GMV ~ After + Station * After | town_id + year_week + week_day, data)
  order_models[[as.character(d)]] <- felm(Orders ~ After + Station * After | town_id + year_week + week_day, data)
}

# Stargazer summary: GMV
stargazer(gmv_models,
          star.cutoffs = c(0.1, 0.05, 0.01, 0.001),
          type = "text",
          no.space = TRUE,
          keep = c("After", "After:Station"),
          keep.stat = "n",
          column.labels = paste0(treat_dists * 1000, "m"),
          title = "Robustness of GMV Estimates by Treatment Distance")

# Stargazer summary: Orders
stargazer(order_models,
          star.cutoffs = c(0.1, 0.05, 0.01, 0.001),
          type = "text",
          no.space = TRUE,
          keep = c("After", "After:Station"),
          keep.stat = "n",
          column.labels = paste0(treat_dists * 1000, "m"),
          title = "Robustness of Order Estimates by Treatment Distance")

```

#### Robustness Check: GMV and Orders by Total Observation Distance ####
```{r warning=FALSE}
obs_dists <- c(0.65, 0.7, 0.75, 0.8)
gmv_obs_models <- list()
order_obs_models <- list()

for (d in obs_dists) {
  data_obs <- filter(data, distance <= d)
  
  gmv_obs_models[[as.character(d)]] <- felm(GMV ~ After + Station * After | town_id + year_week + week_day, data_obs)
  order_obs_models[[as.character(d)]] <- felm(Orders ~ After + Station * After | town_id + year_week + week_day, data_obs)
}

# Stargazer summary: GMV
stargazer(gmv_obs_models,
          star.cutoffs = c(0.1, 0.05, 0.01, 0.001),
          type = "text",
          no.space = TRUE,
          keep = c("After", "After:Station"),
          keep.stat = "n",
          column.labels = paste0(obs_dists * 1000, "m"),
          title = "Robustness of GMV Estimates by Total Observation Distance")

# Stargazer summary: Orders
stargazer(order_obs_models,
          star.cutoffs = c(0.1, 0.05, 0.01, 0.001),
          type = "text",
          no.space = TRUE,
          keep = c("After", "After:Station"),
          keep.stat = "n",
          column.labels = paste0(obs_dists * 1000, "m"),
          title = "Robustness of Order Estimates by Total Observation Distance")
```


### Figure 2(a) Robustness of Estimates on GMV-- Treatment Distance ###
```{r}
distance <- treat_dists
gmv_est <- sapply(gmv_models, function(m) coef(m)["After:Station"])
gmv_std <- sapply(gmv_models, function(m) sqrt(diag(vcov(m)))["After:Station"])

qplot(distance, gmv_est) +
  geom_errorbar(aes(x = distance, ymin = gmv_est - 1.96 * gmv_std, ymax = gmv_est + 1.96 * gmv_std), width = 0.02) +
  ylim(c(-100, 300)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_x_continuous(breaks = seq(0.25, 0.4, 0.05)) +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16, hjust = 0.5)) +
  labs(x = "Treatment Distance (km)", y = "Estimate of GMV")

```

### Figure 2(b) Robustness of Estimates on GMV-- Total Observation Distance ###
```{r}
distance <- obs_dists
gmv_est <- sapply(gmv_obs_models, function(m) coef(m)["After:Station"])
gmv_std <- sapply(gmv_obs_models, function(m) sqrt(diag(vcov(m)))["After:Station"])

qplot(distance, gmv_est) +
  geom_errorbar(aes(x = distance, ymin = gmv_est - 1.96 * gmv_std, ymax = gmv_est + 1.96 * gmv_std), width = 0.02) +
  ylim(c(-100, 300)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_x_continuous(breaks = seq(0.65, 0.8, 0.05)) +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16, hjust = 0.5)) +
  labs(x = "Total Distance (km)", y = "Estimate of GMV")
```

### Figure 3(a) Robustness of Estimates on Number of Orders-- Treatment Distance ###
```{r}
distance <- treat_dists
orders_est <- sapply(order_models, function(m) coef(m)["After:Station"])
orders_std <- sapply(order_models, function(m) sqrt(diag(vcov(m)))["After:Station"])

qplot(distance, orders_est) +
  geom_errorbar(aes(x = distance, ymin = orders_est - 1.96 * orders_std, ymax = orders_est + 1.96 * orders_std), width = 0.02) +
  ylim(c(-0.6, 2)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_x_continuous(breaks = seq(0.25, 0.4, 0.05)) +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16, hjust = 0.5)) +
  labs(x = "Treatment Distance (km)", y = "Estimate of Orders")

```

### Figure 3(b) Robustness of Estimates on GMV-- Total Observation Distance ###
```{r}
distance <- obs_dists
orders_est <- sapply(order_obs_models, function(m) coef(m)["After:Station"])
orders_std <- sapply(order_obs_models, function(m) sqrt(diag(vcov(m)))["After:Station"])

qplot(distance, orders_est) +
  geom_errorbar(aes(x = distance, ymin = orders_est - 1.96 * orders_std, ymax = orders_est + 1.96 * orders_std), width = 0.02) +
  ylim(c(-0.6, 2)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_x_continuous(breaks = seq(0.65, 0.8, 0.05)) +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16, hjust = 0.5)) +
  labs(x = "Total Distance (km)", y = "Estimate of Orders")
```




